Merging Plans of Robots in the asprilo Framework

### 2021-03-20 Documentation/paper.tex
Finished Documentation, Updated Presentation

\section{Analysis of Solution}
There are several benchmarks the solution has been tested on a (a complete list can be found in the appendix). By looking at the results it is obvious that the presented solution is very time inefficient. While it is fast when there is only a small number of robots, a small $horizon$ and a small $c\_nr$, the solution gets very high very fast when these parameters are rising. It does not seem like there is a specific parameter that affects the time the most but that the time rises a lot as soon as there are at least 2 parameters rising. \\
There are several problems that result in this time inefficiency. The first one is that there are two domains whose upper bounds are determined by constants that are chosen at run-time. Especially the usage of the conflict depth makes it very inefficient. Every time there is a conflict, the whole remaining plan has to get pushed back. This results in a lot of predicates that need to be created. Another problematic part is the inertia rule. Since it has to check for every possible time step, conflict depth and robot whether there is a move predicate, it gets very inefficient. However, I have found no way to avoid this problem. \\
Another part that makes the solution inefficient is the usage of choice rules. Since there are several rules where the solver can decide which to choose, a lot of possibilities get created. However, this way of solving has the advantage that theoretically most problems can be solved. 
There are three benchmarks that took too long\footnote{The upper time limit I chose is half an hour} to solve. Two of them have a high number of robots (50 and 30) and need a high horizon as well (about 30 and 60 respectively). The third one only has two robots but a $horizon$ of 19 and a $c\_nr$ of 10. This shows that all the parameters greatly influence the solution time. \\
There are two benchmarks, where the solver returned ``unsatisfiable''. One of them has three robots in a circular corridor (see figure \ref{fig:I1}). This instance is not solvable because the robots need to discard their original plans. As my approach only delays the original plan, it cannot solve such instances. This instance is negligible since it is unlikely that there is a warehouse layout in the real world that does not have any extra space for the robots to dodge to. The second unsolvable instance can be seen in figure \ref{fig:I2}. I do not know why this instance is unsolvable. A similar instance is the one shown in figure \ref{fig:I3}. This instance basically deals with the same problem and can be solved with my solution. Even when reducing the unsolvable instance to just two robots, which makes it even more like the other instance, it is unsolvable. However, this problem seems to be negligible as well since the other benchmarks were solved as expected. This means that only problems that are unlikely to appear in the real world seem to be unsolvable. \\
To summarize, my approach is time inefficient but it seems to be able to solve most problems. This means that it can be used for small instance where the parameters are not very high. The found solution is not optimal because it only solves a conflict the moment it occurs and always completely uses the original plan.

@@

\section{Comparison with other Approaches}
There are 4 other groups that have worked on the same problem. In the appendix, the benchmark results of every solution can be found. For the group consisting of Marius Wawerek and Niklas Kämmer as well as the group consisting of Tom Schmidt, Hannes Weichelt and Jullian Bruns, I have used the python program created by the group of three. The program iteratively finds the minimal horizon for the used merger. \\
The solution of Tarek Ramadan \cite{github1} is able to solve most instances in a short time. The instances with 30 and 50 robots take too long for his solution as well. There are two instances his approach could not solve. Both of these were solvable by my approach. This means, his approach is generally faster but has problems with different instances. \\
The approach of Tom Schmidt, Hannes Weichelt and Julian Bruns \cite{github2} is very fast in the instances it can solve. It is the only approach that can solve the instances with 50 and 30 robots in the designated time frame. The downside is that there are three instances that are unsatisfiable. Benchmark\_1 (the circular shape) is one of them. Another unsolvable instance is the one where the robots have to move away from their original path together which seems to be a problem for this approach. The third unsatisfiable instance is a rather simple problem with only one conflict which makes it weird that it cannot be solved. The approach of this group seems to be very fast. The downside to it is that it cannot solve some instances.  \\
The solution of Marcus Funke and Maximilian Wiedenhöft \cite{github3} seems to have problems similar to mine. It is very time inefficient. Furthermore, there are three instances that cannot be solved. One of those instances is Benchmark\_1 which my approach could not solve either. Their solution can however solve the other instance mine could not. To summarize, their approach is time inefficient as well and there is a similar amount of instances it cannot solve. \\
The solution of Marius Wawerek and Niklas Kämmer \cite{github4} has very short solution times for most instances. The only instances that could not be solved in the designated time were the ones with 30 and 50 robots. There is no instance that is unsolvable. It seems to be the best solution for solving small instances. There does not seem to be any instance it cannot solve. The only problem is that the solving time rises too high if there are too many robots.

>>>>

\section{Analysis of Solution}
There are several benchmarks the solution has been tested on (a complete list can be found in the appendix). By looking at the results it is obvious that the presented solution is very time inefficient. While it is fast when there is only a small number of robots, a small $horizon$ and a small $c\_nr$, the solution time gets very high very fast when these parameters are rising. It does not seem like there is a specific parameter that affects the time the most but that the time rises a lot as soon as there are at least 2 parameters rising. \\
There are several problems that result in this time inefficiency. The first one is that there are two domains whose upper bounds are determined by constants that are chosen at run-time. Especially the usage of the conflict depth makes it very inefficient. Every time there is a conflict, the whole remaining plan has to get pushed back. This results in a lot of predicates that need to be created. Another problematic part is the inertia rule. Since it has to check for every possible time step, conflict depth and robot whether there is a move predicate, it gets very inefficient. However, I have found no way to avoid this problem. \\
Another part that makes the solution inefficient is the usage of choice rules. Since there are several rules where the solver can decide which to choose, a lot of possibilities get created. However, this way of solving has the advantage that theoretically most problems can be solved. 
There are three benchmarks that took too long\footnote{The upper time limit I chose is half an hour} to solve. Two of them have a high number of robots (50 and 30) and need a high horizon as well (about 30 and 60 respectively). The third one only has two robots but a $horizon$ of 19 and a $c\_nr$ of 10. This shows that all the parameters greatly influence the solution time. \\
There are two benchmarks, where the solver returned ``unsatisfiable''. One of them has three robots in a circular corridor (see figure \ref{fig:I1}). This instance is not solvable because the robots need to discard their original plans. As my approach only delays the original plan, it cannot solve such instances. This instance is negligible since it is unlikely that there is a warehouse layout in the real world that does not have any extra space for the robots to dodge to. The second unsolvable instance can be seen in figure \ref{fig:I2}. I do not know why this instance is unsolvable. A similar instance is the one shown in figure \ref{fig:I3}. This instance basically deals with the same problem and can be solved with my solution. Even when reducing the unsolvable instance to just two robots, which makes it even more like the other instance, it is unsolvable. However, this problem seems to be negligible as well since the other benchmarks were solved as expected. This means that only problems that are unlikely to appear in the real world seem to be unsolvable. \\
To summarize, my approach is time inefficient but it seems to be able to solve most problems. This means that it can be used for small instances where the parameters are not very high. The found solution is not optimal because it only solves a conflict the moment it occurs and always completely uses the original plan.

@@

\section{Comparison with other Approaches}
There are 4 other groups that have worked on the same problem. In the appendix, the benchmark results of every solution can be found. For the group consisting of Marius Wawerek and Niklas Kämmer as well as the group consisting of Tom Schmidt, Hannes Weichelt and Julian Bruns, I have used the python program created by the group of three. The program iteratively finds the minimal horizon for the used merger. \\
The solution of Tarek Ramadan \cite{github1} is able to solve most instances in a short time. The instances with 30 and 50 robots take too long for his solution as well. There are two instances his approach could not solve. Both of these were solvable by my approach. This means, his approach is generally faster but has problems with different instances. \\
The approach of Tom Schmidt, Hannes Weichelt and Julian Bruns \cite{github2} is very fast in the instances it can solve. It is the only approach that can solve the instances with 50 and 30 robots in the designated time frame. The downside is that there are three instances that are unsatisfiable. Benchmark\_1 (the circular shape) is one of them. Another unsolvable instance is the one where the robots have to move away from their original path together which seems to be a problem for this approach. The third unsatisfiable instance is a rather simple problem with only one conflict which makes it weird that it cannot be solved. The approach of this group seems to be very fast. The downside to it is that it cannot solve some instances.  \\
The solution of Marcus Funke and Maximilian Wiedenhöft \cite{github3} seems to have problems similar to mine. It is very time inefficient. Furthermore, there are three instances that cannot be solved. One of those instances is Benchmark\_1 which my approach could not solve either. Their solution can however solve the other instance mine could not. To summarize, their approach is time inefficient as well and there is a similar amount of instances it cannot solve. \\
The solution of Marius Wawerek and Niklas Kämmer \cite{github4} has very short solution times for most instances. The only instances that could not be solved in the designated time were the ones with 30 and 50 robots. There is no instance that is unsolvable. It seems to be the best solution for solving small instances. There does not seem to be any instance it cannot solve. The only problem is that the solving time rises too high if there are too many robots.
